### 2020-07-02 related_work.tex
temp

\section{Related Work}
\label{sec-related-work}
\begin{table}[t]
  \caption{A comparison of the state-of-the-arts on shoulder surfing.}
  \vspace{2mm}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
   Reference & Scenarios & Training & distance$^{\mathrm{a}}$ \\
  \hline
  Eiband et al.~\cite{eiband2017understanding}  & naked eye & trained & 1 meter \\
  Kwon et al.~\cite{kwon2013covert}  & naked eye & untrained  & Intimate$^{\mathrm{b}}$\\
Schaub et al.~\cite{schaub2012password} & naked eye & untrained & Intimate\\
  Maggi et al.~\cite{maggi2011poster}  & camera & untrained  & Intimate \\
  \hline
  \hline
  \textbf{\textsf{SRPeek}} & COTS phones & trained  & 1.8 / 6 meter\\
  \hline
  \multicolumn{4}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen.}\\

  \multicolumn{4}{l}{$^{\mathrm{b}}$The attacker stands next to or behind the victim.}\\
  \end{tabular}
  \label{tbl:comparison}
  \end{center}
\end{table}

>>>>

\section{Related Work}
\label{sec-related-work}
\begin{table}[t]
  \caption{A comparison of the state-of-the-arts on shoulder surfing.}
  \vspace{2mm}
  \begin{center}
  \begin{tabular}{ccccc}
  \hline
   Reference & Scenarios   & Accuracy & \begin{tabular}[c]{@{}l@{}}Quantitative \\ Model\end{tabular}& Distance$^{\mathrm{a}}$ \\
  \hline
  Eiband et al.~\cite{eiband2017understanding}  & naked eye & no & no & 1 meter \\
  Kwon et al.~\cite{kwon2013covert}  & naked eye & no & no &-$^{\mathrm{b}}$\\
Schaub et al.~\cite{schaub2012password} & naked eye & no & no & -\\
  Maggi et al.~\cite{maggi2011poster}  & camera & yes  & no &- \\
  \hline
  \hline
  \textbf{\textsf{SRPeek}} & COTS phones & yes & yes  & 1.8 / 6 meter\\
  \hline
  \multicolumn{5}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen.}\\

  \multicolumn{5}{l}{$^{\mathrm{b}}$Distance is uncontrolled; The attacker stands next to or behind the victim.}\\
  \end{tabular}
  \label{tbl:comparison}
  \end{center}
\end{table}
